\Large \bf Polyglots : Crossing Origins by Crossing Formats

### 2013-05-08 main.tex
appendix
Fixed most todos

\paragraph{Internet origins at stake}
The different trust domains
correspond to different Internet origins. A major goal for web
application security is preventing undesired communication across
origins. 
%
With the goal of separating information from the different origins,
today's browsers enforce the \emph{same-origin policy} (SOP). SOP
only allows access between two documents if they share the
origin. In addition, a document can only directly communicate with the
server from which it originates.

@@

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%

Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
We present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

@@

\paragraph{Generalizing polyglots} 
The paper is the first to perform a generalization and systematic study of polyglot
attacks.
We identify the necessary ingredients for polyglot attacks.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins.

@@

By crossing origins we mean being able to request and access content
which is normally restricted under the same-origin policy. 
Recall that SOP only allows two documents accessing each others'
content and resources if they share the origin. Similarly,
a document can only directly communicate with the server from which it originates. 
This is not to be confused with \emph{cross-origin resource sharing} (CORS)~\cite{w3-cors}, which is an 
intentional relaxation of SOP.

@@

Other examples of problematic elements include the \emph{object} and
\emph{embed} tags. These 
tags allow inclusion of resources that might require a 
plug-in to run. As with images, the content handled by the plug-in retains its origin, 
but the browsers are forced to rely on the plug-ins to employ correct security 
measures to prevent information leaks. The plug-in is selected based on the MIME-type of the content, but
because the server delivering the content might not be able to determine its
format, the \emph{object} tag allows a developer to set the type-attribute to guide the
browser in which plug-in to run. When the type attribute is used, the
corresponding plug-in is run regardless of which MIME-type the server returns
and it is up to the plug-in to respond to and handle the content it is served. While the containing page is restricted 
from directly accessing the content handled by the plug-in, a number of plug-ins provide 
an API for interacting with the plug-in and the data. As we will show, this can lead to 
to cross-origin information leaks.

@@

\begin{lstlisting}[label=lst:sample-pdf, caption=Sample PDF file]
%PDF-1.4
1 0 obj
<< /Type /Catalog
   /Outlines 2 0 R
   /Pages 3 0 R
>>
endobj
2 0 obj
<< /Type Outlines
   /Count 0
>>
endobj
3 0 obj
<< /Type /Pages
   /Kids [4 0 R]
   /Count 1
>>
endobj
4 0 obj
<< /Type /Page
   /Parent 3 0 R
   /MediaBox [0 0 612 792]
   /Contents 5 0 R
   /Resources << /ProcSet 6 0 R >>
>>
endobj
5 0 obj
<< /Length 35 >>
stream
   ...Page-marking operators...
endstream
endobj
6 0 obj
   [/PDF]
endobj
xref
0 7
0000000000 65535 f
0000000009 00000 n
0000000074 00000 n
0000000120 00000 n
0000000179 00000 n
0000000300 00000 n
0000000384 00000 n
trailer
<< /Size 7
   /Root 1 0 R
>>
startxref
408
%%EOF
\end{lstlisting}

@@

\subsection{Syntax injection}
\label{sec:pdf-injection}
As the scenario details in Section~\ref{sec:injection}, the attacker in a syntax 
injection attack manipulates a vulnerable service to include PDF syntax in existing content, e.g. HTML-documents.
The PDF syntax is typically injected through user input used by the vulnerable service in the composition of documents.
%
An example of a suitable fragment to inject is shown in Listing~\ref{lst:xml-pdf}.
%
The content is subsequently 
embedded in the attackers page as PDF, as exemplified in Listing~\ref{lst:embed-pdf}.
As mentioned in Section~\ref{sec:pdf-based-polyglots}, the embedded PDF can issue 
requests to the origin it came from, carrying the cookies associated with that origin.
These requests allow for the extraction of sensitive user data that can either be 
communicated back to the attacker, or be leveraged in further attacks.

@@

\subsection{Content smuggling}

@@

Given the extensive capabilities of the PDF format, exploiting a content smuggling 
vulnerability with a PDF-based polyglot attack, can be done without much effort.
To prevent the attack, the 
verification process have to actively search for and remove PDF specific syntax.

@@

\paragraph{XML External Entities}
The PDF JavaScript API includes a method to parse XML documents, called 
XMLData.parse. The XML document being processed may in turn rely on external entities, 
required for the parsing of the document, which the XML parser will request. The request is 
bound to the origin of the document, and the response is included in the XML document. 
The source code of the XML document reflects this response and can be retrieved at a later point. This 
results in a bidirectional communication channel.
%
As the response 
is included in the XML, the result has to be well-formed XML. This puts a 
restriction on the content that can be requested using this method. Considering 
that HTML pages are rarely well-formed this method may be too restricted in practice.

@@

@@

\paragraph{Syntax injection}
The study is based on supplying the websites with the benign minimal PDF in 
Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
The sample contains the essential keywords and tokens required to perform a syntax 
injection based polyglot attack. If these tokens pass through unaltered, the website is 
considered vulnerable. Only public accessible input parameters, those that do not require authentication, 
were tested, which suggests that more websites are likely vulnerable in input that do
requires authentication.

The conclusion is 
that nine websites out of the hundred apply insufficient content filtering with 
respect to the PDF format. Out of the nine found to be vulnerable; three were susceptible to traditional 
XSS and thereby also to PDF polyglot attacks, two were susceptible only to PDF based polyglot attacks, and four applied 
insufficient content filtering, but the input was reflected in a way that prevented exploitation, e.g. the header appeared after 1024 bytes.
%
%, which have the potential of compromising the 
%confidentiality and integrity of the website's users.
%

The two web sites found susceptible only to polyglot attacks and not XSS attacks
are of particular interest. They both employ proper measures to protect properly 
against XSS attacks, and yet fall short in defeating this new breed of attacks.

\begin{enumerate}
\item The first web site reflected user input in an inline  
JavaScript context, inside a string. To prevent cross-site scripting in this 
context, the following measures were taken: the JavaScript string delimiters 
were properly encoded, the backslash character was properly escaped, and the 
string "$<$/script$>$" was removed. None of these measures prevent an attacker 
from injecting valid PDF syntax.
\item The second website reflected the user input in an HTML-comment context. 
The only measure taken to prevent XSS attacks in this context was removing any 
occurrence of the character sequence "--$>$". Again, while successfully preventing 
XSS attacks, this measure is ineffective in preventing an attacker from injecting PDF syntax.
\end{enumerate}

\paragraph{Content smuggling}
Further, a smaller study was conducted, not covering the full Alexa top 100, but 
targeting popular cloud storage services. 
This study is based on polyglot content being uploaded to the service and 
subsequently analyzed to determine which origin it was served under. One major 
enterprise cloud storage service was found to be susceptible to attacks. The service makes an effort to
follow current best practices, see Section~\ref{sec:smuggling-mitigation}, for almost all uploaded content; the exception being the user's 
avatar images that are served under the sensitive origin. An attacker could 
upload a specially crafted avatar image that, when embedded as PDF on the attackers 
web site, can access and modify the contents of the victim's cloud storage.
We are currently advising the service provider to help mitigate this vulnerability.

@@

%1-2 pages 
\bibliographystyle{plain}
\bibliography{literature}
\end{document}

>>>>

\paragraph{Internet origins at stake}
The different trust domains
correspond to different Internet origins. A major goal for web
application security is preventing undesired communication across
origins. 
%
With the goal of separating information from the different origins,
today's browsers enforce the \emph{same-origin policy} (SOP). SOP
only allows access between two documents if they share the
origin. In addition, a document can only directly communicate with the
server from which it originates. 
\todo{More?} Typically a document is considered to be an HTML-page.

@@

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.

\paragraph{Attack vectors}
\todo{Describe general scenario with forward pointer}
We present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

@@

\paragraph{Generalizing polyglot attacks} 
The paper is the first to perform a generalization and systematic study of polyglot
attacks.
We identify the necessary ingredients for polyglot attacks.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins.

@@

By crossing origins we mean being able to request and access content
which is normally restricted under the same-origin policy. 
Recall that SOP only allows two documents accessing each others'
content and resources if they share the origin.
%\todo{More on SOP}
Similarly,
a document can only directly communicate with the server from which it originates. 
This is not to be confused with \emph{cross-origin resource sharing} (CORS)~\cite{w3-cors}, which is an 
intentional relaxation of SOP.

@@

Other examples of problematic elements include the \emph{object} and
\emph{embed} tags. These 
tags allow inclusion of resources that may require a 
plug-in to run. The plug-in is selected based on the MIME-type of the content, but
because the server delivering the content might not be able to determine its
format, the tags allow a developer to set the type-attribute to guide the
browser in which plug-in to run. When the type attribute is used, the
corresponding plug-in is run regardless of the MIME-type provided by the server. 
%
In the event that the provided MIME-type do not match that for which the plug-in is 
designed, e.g., \emph{text/html} for a PDF plug-in, it is up to the plug-in to respond to the content it is served.
Known methods of handling MIME-types, such as content-sniffing, are effective 
in this situation, but they have to be employed by each and every plug-in.
Most plug-ins will disregard the MIME-type of the content and attempt to parse 
it. 
%

As with images, the content handled by the plug-in is executed in the origin it was served from. 
This implies that the containing page is restricted 
from directly accessing the content handled by the plug-in, and that the content can 
communicate freely with the origin it was loaded from. However,  a number of plug-ins provide 
an API for interaction between the plug-in and the document.
The browsers are forced to rely on the plug-ins to employ correct security 
measures. Section~\ref{sec:eval} shows that even state-of-the-art plug-ins fail to properly do so. As we will show, this can lead to 
to cross-origin information leaks.

@@

@@

In recent versions of Adobe Reader certain measures has been taken to prevent 
creating PDF-based polyglots. In accordance with our recommendations Adobe Reader 
has made the parsing more strict by attempting to match the first bytes of the 
file against a set of known signatures. If 
a match is found, the parser will abort loading of the document. The problem of 
this approach is that there are a number of file formats that lack a reliable 
signature, e.g., HTML. Also, for this approach to be reliable, the signature 
must match the signature enforced by other interpreters of the format. A notable 
counter example is the signature used for the JPG format. While the signature is 
correct according to the specification of the format, several JPG interpreters
will allow slightly malformed signatures. Such a malformed signature will bypass 
the check in Adobe Reader and still be rendered correctly in a viewer. This opens up for PDF-based
polyglot attacks.

\subsection{PDF attacks}

As explained in Section~\ref{\todo{ref}} there are two vectors for polyglot 
attacks; \emph{syntax injection} and \emph{content smuggling}. PDF is a suitable 
format for both vectors as it is both a text based format with error tolerant parsing, 
and has widespread acceptance as a document format, often preferred over 
other document formats.

\subsubsection{Syntax injection}
\label{sec:pdf-injection}
As the scenario details in Section~\ref{sec:injection}, the attacker in a syntax 
injection attack manipulates a vulnerable service to include PDF syntax in existing content, e.g. HTML-documents.
The PDF syntax is typically injected through user input used by the vulnerable service in the composition of documents.
%
An example of a suitable fragment to inject is shown in Listing~\ref{lst:xml-pdf}.
%
The content is subsequently 
embedded in the attackers page as PDF, as exemplified in Listing~\ref{lst:embed-pdf}.
As mentioned in Section~\ref{sec:pdf-based-polyglots}, the embedded PDF can issue 
requests to the origin it came from, carrying the cookies associated with that origin.
These requests allow for the extraction of sensitive user data that can either be 
communicated back to the attacker, or be leveraged in further attacks.

@@

\subsubsection{Content smuggling}

@@

Given the extensive capabilities of the PDF format, exploiting a content smuggling 
vulnerability with a PDF-based polyglot attack, can be done without much effort.
To prevent the attack, the 
verification process have to actively search for and remove PDF specific syntax.
The impact of exploitation depends on the payload used in the attack.

@@

\paragraph{XML External Entities}
The PDF JavaScript API includes a method to parse XML documents, called 
XMLData.parse. The XML document being processed may in turn rely on external entities, 
required for the parsing of the document, which the XML parser will request. The request is 
bound to the origin of the document, and the response is included in the XML document. 
The source code of the XML document reflects this response and can be retrieved at a later point,
resulting in a bidirectional communication channel.
%
As the response 
is included in the XML, the result has to be well-formed XML. This puts a 
restriction on the content that can be requested using this method. Considering 
that HTML pages are rarely well-formed this method may be too restricted in practice.

@@

As of version 10.1.5, in accordance with our recommendations,  XML external entities 
has been removed. Thereby the risks of leakage of sensitive information is significantly reduced.

@@

\paragraph{Syntax injection}
The study is based on supplying the websites with the benign minimal PDF in 
Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
The sample contains the essential keywords and tokens required to perform a syntax 
injection based polyglot attack. If these tokens pass through unaltered, the website is 
considered vulnerable. The process has been conducted manually and only input 
parameters on publicly accessible pages, those that do not require authentication, 
were tested. Considering that most inputs are available only to authenticated 
users, the results suggests that more websites are likely vulnerable in input that do
require authentication.

The conclusion is 
that nine websites out of the hundred apply insufficient content filtering with 
respect to the PDF format. Out of the nine found to be vulnerable; five were 
susceptible to PDF based polyglot attacks, and four applied 
insufficient content filtering, but the input was reflected in a way that 
prevented exploitation, e.g. the header appeared after 1024 bytes.
%
%, which have the potential of compromising the 
%confidentiality and integrity of the website's users.
%

Three of the five vulnerable web sites could also be determined to be vulnerable to 
traditional XSS attacks in the same input parameters. 
The remaining two web sites found susceptible only to polyglot attacks and not XSS attacks
are of particular interest since they employ proper measures to protect 
against XSS attacks, and yet fall short in defeating this new breed of attacks.

\begin{enumerate}
\item The first web site reflected user input in an inline  
JavaScript context, inside a string. To prevent cross-site scripting in this 
context, the following measures were taken: the JavaScript string delimiters 
and the backslash character were properly escaped, and the 
string "$<$/script$>$" was removed. These measures are sufficient to protect against XSS attacks, 
but do not prevent an attacker 
from injecting valid PDF syntax.
\item The second website reflected the user input in an HTML-comment context. 
The only measure taken to prevent XSS attacks in this context was removing any 
occurrence of the character sequence "--$>$". Again, while successfully preventing 
XSS attacks, this measure is ineffective in preventing an attacker from injecting PDF syntax.
\end{enumerate}

\paragraph{Content smuggling}
Further, a smaller study was conducted, not covering the full Alexa top 100, but 
targeting popular cloud storage services. 
This study is based on polyglot content being uploaded to the service and 
subsequently analyzed to determine which origin it was served under. Two major 
enterprise cloud storage services were found to be susceptible to attacks. Both service makes an effort to
follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but fail to cover scenarios for content upload.

The first service serves almost all uploaded content from a sandboxed origin; the exception being the user's 
avatar image that are served under the sensitive origin. An attacker could 
upload a specially crafted avatar image that, when embedded as PDF on the attackers 
web site, can access and modify the contents of the victim's cloud storage.

The second service lets the user publish a public link to an HTML 
representation of the content. The content is served under the sensitive origin 
and is therefore carefully processed to prevent 
generation of malicious HTML, but fails to take other formats into account.
A specially crafted file will result in the generation of valid PDF syntax that, when embedded as PDF on the attackers 
web site, can access and modify the contents of the victim's cloud storage.

We are currently advising both service providers to help mitigate these vulnerabilities.

@@

%1-2 pages 
\bibliographystyle{plain}
\bibliography{literature}

\appendix

\section{Sample PDF file}
\begin{lstlisting}[label=lst:sample-pdf, caption=Sample PDF file]
%PDF-1.4
1 0 obj
<< /Type /Catalog
   /Outlines 2 0 R
   /Pages 3 0 R
>>
endobj
2 0 obj
<< /Type Outlines
   /Count 0
>>
endobj
3 0 obj
<< /Type /Pages
   /Kids [4 0 R]
   /Count 1
>>
endobj
4 0 obj
<< /Type /Page
   /Parent 3 0 R
   /MediaBox [0 0 612 792]
   /Contents 5 0 R
   /Resources << /ProcSet 6 0 R >>
>>
endobj
5 0 obj
<< /Length 35 >>
stream
   ...Page-marking operators...
endstream
endobj
6 0 obj
   [/PDF]
endobj
xref
0 7
0000000000 65535 f
0000000009 00000 n
0000000074 00000 n
0000000120 00000 n
0000000179 00000 n
0000000300 00000 n
0000000384 00000 n
trailer
<< /Size 7
   /Root 1 0 R
>>
startxref
408
%%EOF
\end{lstlisting}

\end{document}
